%-------------------------
% Resume in Latex
% Author : Drew Johnson
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------------
%---  Resume STARTS HERE  ---


\begin{document}

%----------HEADING-----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.drewj.dev/}{\Large Drew Johnson}} & \href{mailto:drewjohnsongt@gmail.com}{DrewJohnsonGT@gmail.com}\\
  \href{https://drewj.dev/}{https://www.drewj.dev} & 404-825-2866 \\
\end{tabular*}


%-----------EDUCATION--------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Bachelor of Science in Computer Science}{Aug 2013 -- Aug 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-------
\section{Experience}
  \resumeSubHeadingListStart
  
      \resumeSubheading
      {The Home Depot}{Atlanta, GA}
      {Senior Software Engineer}{May 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Full Stack TypeScript}
          {Developed suite of React frontends and Node/Express/TypeORM layered microservice APIs in TypeScript. Adhered to TypeScript best practices to maximize cross resource models and code sharing.}
        \resumeItem{Test Driven Development}
          {Focused heavily on TDD principles, leveraging various tools for E2E, integration, and unit testing. Integrated testing with CI/CD processes including augmented coverage reporting.}
        \resumeItem{Cloud Architecture and SRE}
          {Created and managed CI/CD pipelines and infrastructure for all applications both on-premise and cloud based. Engineered for high latency consumption by B2B/B2C consumers.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Delta Air Lines}{Atlanta, GA}
      {Senior Software Engineer}{Sep 2019 -- May 2020}
      \resumeItemListStart
        \resumeItem{Cloud Architecture and Development}
          {Guided development architecture of Delta's first AWS cloud migration project, implementing real-time data streaming from on-premise sources 
          following serverless and cloud native models.}
        \resumeItem{Data Ingestion and Streaming}
          {Developed on-premise and counterpart cloud applications/functions for real-time, multi-source customer data 
          ingestion, standardization, and consolidation around centralized IDs.}
        \resumeItem{Data Engineering}
          {Produced new and updating existing data mappings and flows for data sources and implemented distributed 
          database solutions accounting for scalable fault/exception tolerance.}
        \resumeItem{BDD and Functional Testing}
          {Automated internal unit and integration testing practices, increasing test coverage by over 75\%, 
          saving hundreds of monthly hours manual testing.}
      \resumeItemListEnd

    \resumeSubheading
      {Meridian Business Services}{Overland Park, KS}
      {Lead Software Engineer}{Oct 2017 -- Sep 2019}
      \resumeItemListStart
        \resumeItem{Development Lead}
          {Lead development efforts supporting company's 2-year 500\% growth, 
          establishing and maintaining core engineering best practices while delivering effective and efficient code.}
        \resumeItem{Web Solutions}
          {Architected and developed ERP/CRM customizations for over 50 clients including extensive 
          third-party integrations/API development, backend workflow automations, and full-stack web-app development}
        \resumeItem{CI/CD and Testing}
          {Designed and developed custom CI/CD platform for custom ERP/CRM scripts, enabling development best practice 
          adherence and increasing effective code delivery throughput 200\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Schenck Process}{Kansas City, MO}
      {Lead Software Engineer (Contract)}{Oct 2018 -- Apr 2019}
      \resumeItemListStart
        \resumeItem{Full-Stack App Design/Development}
          {Architected, developed, and implemented engineering product specification/sizing tool, saving hundreds of 
          monthly engineer hours and preventing company liability issues.}
        \resumeItem{Frontend Configurator}
          {React/Redux configurator adhering to the NFPA 68 standard. Performing complex mathematical operations derived from Mathcad worksheets 
          and displaying solutions in real time.}

      \resumeItemListEnd
    \resumeSubheading
      {Federal Aviation Administration}{Hampton, GA}
      {Software Engineer (Contract)}{Mar 2018 -- Dec 2018}
      \resumeItemListStart
        \resumeItem{Serverless Application}
          {Designed/developed scheduling PWA for use by over 100 Atlanta based FAA employees. 
          React/Redux frontend and Node Lambda backend with GraphQL API including role based access control.}
        \resumeItem{Database Solution}
          {Automated manual process of identifying facility landline emergency call location to aid in dispatch of 911 services. 
          Reduced telephone specialist operator effort by dozens of hours a month.}
      \resumeItemListEnd

    \resumeSubheading
      {DSI Global}{Kansas City, MO}
      {Software Developer (Contract)}{Dec 2017 -- Dec 2018}
      \resumeItemListStart
        \resumeItem{React/Redux Implementation}
          {Proposed and lead implementation of React with Redux in new production applications 
          and refactoring of older products from plain HTML with monolithic CSS.}
        \resumeItem{Backend REST API}
          {Refactored RESTful API utilizing customized SQL queries resulting in 250\% reduction in client request time and requiring half the original client requests.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%----------PROJECTS----------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{NetSuite Login Chrome Extension}
%      {Chrome extension to facilitate provisioning and use of shared NetSuite accounts with real-time login 
%      management and access control. Utilized by engineering team with around 20 active users.}
%    \resumeSubItem{Project FORM}
%      {React Native application utilizing pose estimation/detection models to provide automated exercise feedback designed for injury prevention. 
%      Both offline and cloud data processing.}
%  \resumeSubHeadingListEnd


%----PROGRAMMING SKILLS------
\section{Skills}
 \textbf{Languages}{: JavaScript, TypeScript, HTML/CSS, Python, Scala, Java, SQL, GraphQL}
 \\
 \textbf{Frameworks/Tools}{: React, Node, AWS, GCP, Gatsby/Next, Cypress, Spark, Hadoop, Kafka}


%----------------------------
\end{document}